\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{graphics}
\setlength{\parindent}{0pt}

\title{Final Exam}
\date{}

\begin{document}

\maketitle

\section{General Notes}
To save paper, I've left just enough space between problems for you to write the answer down. Please use separate sheets of paper to record your work. Please turn them in stapled, with work for each problem circled and labelled by problem number. \\

Please note that showing work is necessary. You don't have to show every tiny step, but you are expected to demonstrate mastery of a technique. This also allows me to give partial credit even when the answer is wrong. You are strongly encouraged to check your answers thoroughly with any extra time you have. Please put only answers on this test sheet.\\

Good luck !

\section{Polynomial Multiplication and Division}

(1) Evaluate the product $[(4p-3)+ 6q][(4p-3) -6q]$.\\\\\\\\






(2) Divide $6m^3-m^2+8m + 5$ by $3m-2$.\\\\\\\\\\\

(3) Divide $4x^3-2x^2-4x + 2$ by $2x^2-2$.\\\\\\\\\

\section{Linear Equations}

(4) Solve the equation $4(3x-5) = 8 - (2x + 6)$.\\\\\\\\\\\


(5) Solve the equation $\frac{4x+2}{3} + \frac{1}{6}x = \frac{1}{2}x-\frac{5}{6}$.\\\\\\\\\\\

(6)  A chemist needs a 15 percent solution of alcohol. She has a 10 percent solution and a 20 percent solution on hand (as much as she might need of either). How many liters of the 10 percent solution should she add to 2 liters of the 20 percent solution in order to get a 15 percent solution?\\\\\\\\

\section{Quadratic Equations}


(7) Solve the equation $x^2 -5x  = -3$.\\\\\\\\\\\\\\\\


(8) Solve the equation $x^2 -x = 1$.\\\\\\\\\\\\\\\\





(9) Solve the equation $x^2 - 144 = 0$.\\\\\\\\\\\\\\\



(10) Solve the equation $\frac{1}{10}x^2 -\frac{1}{2}x + \frac{3}{10} = 0$.


\end{document}
